Fifteen years of decentralization attempts

### 2014-03-24 paper.tex
Removed sentence about filtering
Remove commented out paragraphs
Fix indent
Typo

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	Ever since the introduction of the internet, it has been void of any privacy. A number of anonymous communication overlay networks exist whose aim it is to provide privacy to its users. However, due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous. We list reasons for having anonymous networks, discern the problems in achieving decentralization and sum up the biggest initiatives in the field and their current status. To do so, we use one exemplary network, the Tor network. We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity. The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.

	%In the emerging world of ubiquitous internet access, void of any privacy, there are a number of anonymous communication overlay networks whose aim it is to provide privacy to its users. Due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous. This technical report lists reasons for having anonymous networks, discerns the problems in achieving decentralization in anonymous networks and sums up the biggest competitors in the field and their current status. To do so, we use one exemplary network, the Tor network. We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity. The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.

	%There are quite a few distributed anonymous communication networks such as Tor, yet when it comes to decentralized anonymous systems the numbers are rather small and certain problems arise. In this technical report we explain how Tor works and which attacks are possible and which vulnerabilities currently exist in Tor. After that, we talk about why would like to decentralize peer-to-peer networks, what the difficulties are with decentralizing networks and show which projects have made an attempt to decentralize or are already (partially) decentralized. Finally, we provide a table in where we compare these projects against each other, which will also be public available on the Github page mention in this report.
\end{abstract}

@@

		%As described in the previous section, data on the Tor networks travels over circuits. The data travels over the circuit in fixed-size cells that are 512 bytes long. Each cell has a header and a payload. The header consists of a number that identifies the circuit the cell travels on and a command that indicates what to do with the cell’s payload.

		%Before a circuit can be established, a path has to be chosen. The current path selection algorithm in Tor selects nodes based on the bandwidth of the nodes \cite{wang2012congestion}. Nodes that have more bandwidth, have a higher probability to be chosen for the circuit setup, however, the same node can't be used more than once in a circuit.

@@

		\end{itemize}

		The directory service generates overhead on the network. Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance. In conclusion, this means that we would like to see Tor decentralized. Although much research has been done on the decentralization of Tor, it still uses centralized components today.

@@

			Unless hidden services are used, content travels unencrypted through a Tor exit node. Users running a Tor exit node could be held responsible for distributing illegal content. The possibility of being seen as the originator of illegal content refrains users from running an exit node. A possible solution could be to filter the illegal content from the legal content. While content filtering could be a possible solution, it is an open question whether filtering is in line with the principles of Tor and the internet. We think however that filtering the content on Tor could make more users run an exit node and thus improve the quality of the network.

@@

	\subsection{Other decentralized systems}
		Some other decentralized peer-to-peer systems has been developed, focussing on anonymity. An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible. The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms. Users are able to send and receive unicast, multicast and anycast messages anonymously. The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages. A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
	Ever since the introduction of the internet, it has been void of any privacy. A number of anonymous communication overlay networks exist whose aim it is to provide privacy to its users. However, due to the nature of the internet, there is major difficulty in getting these networks to become both decentralized and anonymous. We list reasons for having anonymous networks, discern the problems in achieving decentralization and sum up the biggest initiatives in the field and their current status. To do so, we use one exemplary network, the Tor network. We explain how Tor works, what vulnerabilities this network currently has, and possible attacks that could be used to violate privacy and anonymity. The Tor network is used as a key comparison network in the main part of the report: a tabular overview of the major anonymous networking technologies in use today.
\end{abstract}

@@

@@

		\end{itemize}
			The directory service generates overhead on the network. Replacing this central authority with a decentralized component, could reduce the overhead of the network and improve performance. In conclusion, this means that we would like to see Tor decentralized. Although much research has been done on the decentralization of Tor, it still uses centralized components today.

@@

			Unless hidden services are used, content travels unencrypted through a Tor exit node. Users running a Tor exit node could be held responsible for distributing illegal content. The possibility of being seen as the originator of illegal content refrains users from running an exit node. A possible solution could be to filter the illegal content from the legal content. While content filtering could be a possible solution, it is an open question whether filtering is in line with the principles of Tor and the internet.

@@

	\subsection{Other decentralized systems}
		Some other decentralized peer-to-peer systems have been developed, focussing on anonymity. An example of such a system is AP3 (Anonymizing Peer-to-Peer Proxy) \cite{mislove2004ap3} which makes cooperative, decentralized anonymous communication possible. The AP3 system provides clients with three primitives: anonymous message delivery, anonymous channels and secure pseudonyms. Users are able to send and receive unicast, multicast and anycast messages anonymously. The strategy that AP3 is using for message delivery is similar to that of Tarzan: it relies on a network of peers to forward messages. A node along the request path, does not know whether the node from which it receives a message is the message's originator or simply another forwarding peer.
